\chapter{Characters}
\begin{itemize}
\item[\ding{100}] \textbf{Bob Cratchit}, clerk to Ebenezer Scrooge.
\item[\ding{101}] \textbf{Peter Cratchit}, a son of the preceding.
\item[\ding{102}] \textbf{Tim Cratchit (\enquote*{Tiny Tim})}, a cripple, youngest son of Bob Cratchit. 
%the enquote* forces the use of enquote's currently set INNER quotes. Since I'm using British style quotations, inner quotes are "", which is what I want.
\item[\ding{100}] \textbf{Mr Fezziwig}, a kind-hearted, jovial old merchant.
\item[\ding{101}] \textbf{Fred}, Scrooge's nephew.
\item[\ding{102}] \textbf{Ghost of Christmas Past}, a phantom showing things past.
\item[\ding{100}] \textbf{Ghost of Christmas Present}, a spirit of a kind, generous, and hearty nature.
\item[\ding{101}] \textbf{Ghost of Christmas Yet to Come}, an apparition showing the shadows of things which yet may happen.
\item[\ding{102}] \textbf{Ghost of Jacob Marley}, a spectre of Scrooge's former partner in business.
\item[\ding{100}] \textbf{Joe}, a marine-store dealer and receiver of stolen goods.
\item[\ding{101}] \textbf{Ebenezer Scrooge}, a grasping, covetous old man, the surviving partner of the firm of Scrooge and Marley.
\item[\ding{102}] \textbf{Mr Topper}, a bachelor.
\item[\ding{100}] \textbf{Dick Wilkins}, a fellow apprentice of Scrooge's.
\item[\ding{101}] \textbf{Belle}, a comely matron, an old sweetheart of Scrooge's.
\item[\ding{102}] \textbf{Caroline}, wife of one of Scrooge's debtors.
\item[\ding{100}] \textbf{Mrs Cratchit}, wife of Bob Cratchit.
\item[\ding{101}] \textbf{Belinda and Martha Cratchit}, daughters of the preceding.
\item[\ding{102}] \textbf{Mrs Dilber}, a laundress.
\item[\ding{100}] \textbf{Fan}, the sister of Scrooge.
\item[\ding{101}] \textbf{Mrs Fezziwig}, the worthy partner of Mr Fezziwig.
\end{itemize}
